Surrogate Modelling of the Tritium Breeding Ratio

### 2020-10-07 talk_ucl_cdt_201008/adaptive.tex
rework background slide, add neat illustration
add slide numbers

        How can we take advantage of surrogate information content \textit{during training} to reduce sample quantity? \newline

        We developed a new technique:
        \vspace{-5pt}
        \begin{enumerate}
        \item Construct surrogate quality distribution by nearest- neighbour interpolation.
        \item Draw candidate samples by quality using MCMC.
        \item Include samples with greatest separation from neighbours.
        \item Repeat!
        \end{enumerate}
      \column{6cm}
      \includegraphics[width=8cm]{qassplan}

@@

\begin{frame}
	\frametitle{Application on Toy Theory}
	Toy functional TBR theory with wavenumber n, and qualitatively comparable ANN performance to Paramak:
	\begin{align*}
		\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
	\end{align*}

@@

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{0.5em}
		Evaluation set:
		\begin{itemize}
		    \item Adaptive samples
		    \item Generated during runtime
		\end{itemize}
		Validation set:
		\begin{itemize}
		    \item Uniform random samples
		    \item Generated independently
		\end{itemize}
		\vspace{15pt}

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-10pt}
    \begin{center}
    \includegraphics[width=12cm]{qassresult}
    \end{center}

    $60\%$ decrease in MAE for validation set (dashed) \newline
    Equivalently, $6\%$ decrease in samples needed for same accuracy

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-10pt}
    \begin{center}
    \includegraphics[width=12cm]{qassincr}
    \end{center}

>>>>

        How to take advantage of surrogate information content \textit{during training} to reduce sample quantity? \newline

		We developed \alert{a new technique:}
        \vspace{-1em}
        \begin{enumerate}
        \item Construct surrogate quality distribution by nearest- neighbour interpolation.
        \item Draw candidate samples by quality using MCMC.
        \item Include samples with greatest separation from neighbours.
        \item Repeat!
        \end{enumerate}
      \column{6cm}
      \includegraphics[width=8cm]{qassplan}

@@

\begin{frame}
	\frametitle{Application on Toy Theory}
	Toy functional TBR theory with wavenumber $n$, and qualitatively comparable ANN performance to Paramak:
	\begin{align*}
		\text{TBR}_\text{toy} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
	\end{align*}

@@

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{-0.5em}
		Evaluation set:
		\begin{itemize}
		    \item Adaptive samples
		    \item Generated during runtime
		\end{itemize}
		\vspace{0.5em}
		Validation set:
		\begin{itemize}
		    \item Uniform random samples
		    \item Generated independently
		\end{itemize}
		\vspace{15pt}

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-20pt}
    \begin{center}
    \includegraphics[width=12cm]{qassresult}
    \end{center}

	\alert{$60\%$ decrease} in MAE for validation set (dashed) \newline
	Equivalently, \alert{$6\%$ decrease} in samples needed for same accuracy

@@

\begin{frame}
    \frametitle{Adaptive Sampling: Results}
    \vspace{-20pt}
    \begin{center}
    \includegraphics[width=12cm]{qassincr}
    \end{center}
